---
title: "HW3_Unit3_DSHAH"
author: "Dhyan Shah"
date: "1/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dhyan Shah - 47998760
## Live Session Unit 03 assignment
## MSDS 6306-402

## Question 1 - GitHub Cloning ##

    ## setwd("~/Desktop/DoingDataScience/Unit3/HW3_2"
    ## git clone https://github.com/awesomedata/awesome-public-datasets.git
    ## ls
    ## cd 

## Question 2 - Data Summary  ##
    ## 2.a.
```{r titanic}
df <- read.csv("titanic.csv")
str(df)
head(df)
summary(df)
## print(df)


is.data.frame(df)

## print(df$Sex)
summary(df$Sex)

fem <- subset(df, df$Sex == "female")
## print(fem)

mel <- subset(df, df$Sex == "male")
## print(mel)


```

# Question 2 - Data Summary  ##
  ## 2.b. 

```{r}
table(df$Sex)
table(df$Age)
table(df$Fare)
table(df$Survived)
table(df$Survived, df$Age)
table(df$Survived, df$Age, df$Sex)
table(df$Pclass, df$Survived)

barplot(table(df$Sex), xlab="Sex", ylab="Frequency", main="Titanic Passanger Gender Frequency", col="violet")
```

# Question 2 - Data Summary  ##
  ## 2.c.

```{r}


sapply(df, class)
tapply(df$Age, df$Fare, mean, is.na = TRUE)
tapply(df$Survived, df$Age, mean, is.na = TRUE)
tapply(df$Survived, df$Fare, mean, is.na = TRUE)

```

# Question 3 - Function Building  ##
  ## 3.a.
```{r}  
read.csv("sleep_data_01.csv")
fb <- read.csv("sleep_data_01.csv")
str(fb)
table(fb$Age)
Med_Age <- median(table(fb$Age))
print(Med_Age)

table(fb$Duration)
Min_Dur <- min(table(fb$Duration))
print(Min_Dur)

Max_Dur <- max(table(fb$Duration))
print(Max_Dur)

Mean_RSES <- mean(table(fb$RSES))
print(Mean_RSES)

sd_RSES <- sd(table(fb$RSES))
print(sd_RSES)

tapply(fb$Age, fb$RSES, mean, is.na = TRUE)
tapply(fb$Age, fb$Duration, mean, is.na = TRUE)
tapply(fb$Age, fb$RSES, sd, na.rm = FALSE)
```
# Question 3 - Function Building  ##
  ## 3.b.
  
```{r} 
## Range 
table(fb$Duration)
ran_duration <- range(table(fb$Duration))
r_duration <- (max(ran_duration) - min(ran_duration))
print(r_duration)

xdf <- c(Med_Age, Mean_RSES/5, sd_RSES/5)
print(xdf)

ydf <- c(xdf, r_duration)
print(ydf)

## report <- data.frame(xdf, ydf)

report <- data.frame(Med_Age, Mean_RSES/5, 
                     sd_RSES/5, r_duration)
print(report)
```
# Question 3 - Function Building  ##
  ## 3.c.
```{r} 
 ## c. change the column name of data frame to MedianAge, SelfEsteem, SE_SD, and DurationRange.
report <- data.frame(MedianAge=Med_Age, SelfEsteem=Mean_RSES, SE_SD=sd_RSES, DurationRange=r_duration)
print(report) 
```

# Question 3 - Function Building  ##
  ## 3.d.
```{r} 
 ## d. round the report to at most 2 digit. 
round(report, digits = 2)
```

# Question 3 - Function Building  ##
  ## 3.d.
```{r} 
  ## e. run function on sleep data (sleep_data01.csv), show output 
```

# Question 4 - FiveThirtyEightData  ##
  ## 4.a.
```{r} 
   ## HW3_2 Dhyan$ git clone https://github.com/rudeboybert/fivethirtyeight
# install.packages("fivethirtyeight")
# data(package = "fivethirtyeight")
```
# Question 4 - FiveThirtyEightData  ##
  ## 4.b.
```{r} 
   library(fivethirtyeight)
data(college_recent_grads)
head(college_recent_grads)
#View(college_recent_grads)
df <- college_recent_grads
```
# Question 4 - FiveThirtyEightData  ##
  ## 4.c.
```{r} 
   ??college_recent_grads
## https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```
# Question 4 - FiveThirtyEightData  ##
  ## 4.d.
```{r} 
dim(df)
colnames (df, do.NULL = FALSE, prefix = "col")
```

# Question 5 - Data Summary  ##
  ## 5.a.
```{r} 
  ## 5.a. Column Names, Column Counts 
colnames (df, do.NULL = FALSE, prefix = "col")
ncol(df)
```

# Question 5 - Data Summary  ##
  ## 5.b.
```{r} 
 ## 5.b. count each unique major_category, 

library(plyr)
major_count<- count(df$major_category)
print(major_count)

## Reference for 5.b. 
  ## https://www.tutorialspoint.com
  ## https://cran.r-project.org/doc/contrib/Paradis-rdebuts_en.pdf
  ## https://stackoverflow.com
  ## RStudio Help
  ## Noelle Brown :) THANK YOU!!
```


# Question 5 - Data Summary  ##
  ## 5.c.
```{r} 
  library(ggplot2)

ggplot(data=major_count, aes(x=major_count$x, y=major_count$freq, xlab = "Frequncy", ylab = "Majors", ,main = "Number of Majors"))+geom_bar(stat = "identity", col = "yellow")+coord_flip()

```

# Question 5 - Data Summary  ##
  ## 5.d.
```{r} 
 xf <- data.frame(college_recent_grads)
write.table(xf, file="collegerecentgrads.csv", sep=",", row.names = FALSE, quote = FALSE)
```



## Question 6 - Codebook ##
  ## 6.a,b,c,d
```{r} 
## http://github.com/dhyanshah/SMU_MSDS_6306_HW/README.md
```

## Including Plots

You can also embed plots, for example:

```{r, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
